---
title: "tidyverse_speedrun"
author: "Hannah E. Houts"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Tidyverse?
"The tidyverse is an opinionated collection of R packages designed for data science. 
All packages share an underlying design philosophy, grammar, and data structures."

## Helpful hotkeys- 
cmd-shift-m or ctrl-shift-m will make an r Pipe
cmd-opt-i or ctrl-opt-i will make an r code chunk
hold opt key while dragging with mouse for vertical edit/highlighting


## Install and load packages

```{r}
#install.packages(tidyverse)
#install.packages(janitor)
#install.packages(here)
#install.packages(palmerpenguins)
```


```{r, message=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(palmerpenguins)
```


## Load data

use tidyverse `read_csv`

```{r}
supers <- read_csv("data/heroes_information.csv")
```

## quick summaries

#### column names
```{r}
names(supers)
```

get rid of spaces? get rid of capitalization?
```{r}
supers <- clean_names(supers)

names(supers)
# clean_names() is in the janitor package.
# You can also run like this
# janitor::clean_names()
```




data summaries:

```{r}

### structure, 2/10
#str(supers)

### dimensions, 2/10
#dim(supers)

### glimpse, 8/10
### gives dim, col names, col types, and head of cols. ugly
#glimpse(supers)


### summary, 9.5/10
### gives info about each column. kind of ugly
#summary(supers)

### tabyl, 8/10
### gives info about specified column, from janitor package
tabyl(supers$eye_color)
```


### reducing columns & rows with select() and filter()



```{r}
names(supers)
```



```{r}
supers_select <- supers %>% 
  select(name, hair_color, eye_color, skin_color)

names(supers_select)
```

```{r}
supers_select <- supers %>% 
  select(-publisher)

names(supers_colors)
```